Limited predictability of amino acid substitutions in seasonal influenza viruses

### 2021-01-10 article.tex
Change top/bottom -> left/right in SI

	\begin{figure}
		\centering
		\includegraphics[width=0.9\textwidth]{SM_figures/simulation.png}
		\caption{Fixation probability as a function of frequency for the simulations discussed in the main text. \textbf{Top:} Simulation without antibodies. The three colored curves reflect different rate of change for the fitness landscape. Visual inspection of the frequency trajectories indicates a typical sweep time of $\sim400$ generations. \textbf{Bottom:} Simulation with antibodies. The different colored curves indicate the rate at which antibodies are introduced. }
		\label{fig:simulations}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=0.9\textwidth]{SM_figures/simulation_fitness.png}
		\caption{Fixation probability as a function of frequency for the simulations discussed in the main text, with trajectories stratified according to real fitness values. ``High'' and ``low'' fitness classes are defined with respect to the median value. \textbf{Top:} Simulation without antibodies and with changes to the fitness landscape every $dt=10$ generations. \textbf{Bottom:} Simulation with antibodies, with a new antibody every $dt=10$ generations. }
		\label{fig:simulations_fitness}
	\end{figure}

>>>>

	\begin{figure}
		\centering
		\includegraphics[width=0.9\textwidth]{SM_figures/simulation.png}
		\caption{Fixation probability as a function of frequency for the simulations discussed in the main text. \textbf{Left:} Simulation without antibodies. The three colored curves reflect different rate of change for the fitness landscape. Visual inspection of the frequency trajectories indicates a typical sweep time of $\sim400$ generations. \textbf{Right:} Simulation with antibodies. The different colored curves indicate the rate at which antibodies are introduced. }
		\label{fig:simulations}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=0.9\textwidth]{SM_figures/simulation_fitness.png}
		\caption{Fixation probability as a function of frequency for the simulations discussed in the main text, with trajectories stratified according to real fitness values. ``High'' and ``low'' fitness classes are defined with respect to the median value. \textbf{Left:} Simulation without antibodies and with changes to the fitness landscape every $dt=10$ generations. \textbf{Right:} Simulation with antibodies, with a new antibody every $dt=10$ generations. }
		\label{fig:simulations_fitness}
	\end{figure}
